Stability in human interaction networks: primitive typology of vertex, prominence of measures and activity statistics

### 2015-03-01 paper.tex
alteração no titulo de subseção

\subsection{Scalable fat-tail structure: constancy of participants fraction in the connective sectors}\label{subsec:pih}
There is a concentration of hub activity and of vertex with few connections. Table~\ref{autores} is dedicated to exposing this well known and expected distribution of activity among participants.

>>>>

\subsection{Scalable fat-tail structure: constancy of membership fractions in the connective sectors}\label{subsec:pih}
There is a concentration of hub activity and of vertex with few connections. Table~\ref{autores} is dedicated to exposing this well known and expected distribution of activity among participants.
